---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# geoDK

The goal of geoDK is to make it easy to use danish GIS data in R.

## Installation

You can install geoDK from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mikkelkrogsholm/geoDK")
```

## Polygons

geoDK contains polygon data for a range of danish administrative areas. It has data for: 

* parishes
* zip codes
* municipalities
* regions
* police districts
* jurisdictions
* constituencies

Let me show you a few examples. 

#### First load packages
```{r example1_load}
library(geoDK)
library(ggplot2)
library(ggthemes)
```

#### Plot regions
```{r regions}
dk_regions <- geo_get_spatial("Danish regions")

df_regions <- make_tidy_poly(dk_regions)

ggplot(df_regions) +
  geom_polygon(aes(x = lng, y = lat, group = area, fill = regionkode),
               color = "black", show.legend = FALSE) +
  coord_cartesian() +
  theme_map()
```

#### Plot municipalities
```{r municipalities}
dk_municipalities <- geo_get_spatial("Danish municipalities")

df_municipalities <- make_tidy_poly(dk_municipalities)

ggplot(df_municipalities) +
  geom_polygon(aes(x = lng, y = lat, group = area, fill = komkode),
               color = "black", show.legend = FALSE) +
  coord_cartesian() +
  theme_map()
```

#### Plot police districts
```{r police_districts}
dk_police_districts <- geo_get_spatial("Danish police districts")

df_police_districts <- make_tidy_poly(dk_police_districts)

ggplot(df_police_districts) +
  geom_polygon(aes(x = lng, y = lat, group = area, fill = polkr_nr),
               color = "black", show.legend = FALSE) +
  coord_cartesian() +
  theme_map()
```

#### Plot zip codes
```{r zip_codes}
dk_zip_codes <- geo_get_spatial("Danish zip codes")

df_zip_codes <- make_tidy_poly(dk_zip_codes)

ggplot(df_zip_codes) +
  geom_polygon(aes(x = lng, y = lat, group = area, fill = postnr_txt),
               color = "black", show.legend = FALSE) +
  coord_cartesian() +
  theme_map()
```
