---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# geoDK

The goal of geoDK is to make it easy to use danish GIS data in R.

## Installation

You can install geoDK from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mikkelkrogsholm/geoDK")
```

## Polygons

geoDK contains polygon data for a range of danish administrative areas. It has data for: 

* parishes
* zip codes
* municipalities
* regions
* police districts
* jurisdictions
* constituencies

Let me show you a few examples. 

#### First load packages
```{r example1_load}
library(geoDK)
library(leaflet)
```

#### Plot regions
```{r}
data("geo_reg")
geo_reg@data$regionkode <- as.numeric(geo_reg@data$regionkode)

pal <- colorNumeric(
  palette = "Blues",
  domain = geo_reg$regionkode)

leaflet(geo_reg) %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
              color = ~pal(regionkode))
```

#### Plot municipalities
```{r}
data("geo_mun")
geo_mun@data$komkode <- as.numeric(geo_mun@data$komkode)

pal <- colorNumeric(
  palette = "Reds",
  domain = geo_mun$komkode)

leaflet(geo_mun) %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
              color = ~pal(komkode))
```

#### Plot police districts
```{r}
data("geo_pol")
geo_pol@data$polkr_nr <- as.numeric(geo_pol@data$polkr_nr)

pal <- colorNumeric(
  palette = "Set3",
  domain = geo_pol$polkr_nr)

leaflet(geo_pol) %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
              color = ~pal(polkr_nr))
```

